Standalone Tactics using OpenTheory

### 2012-02-11 paper.tex
bit more sec 4

<idea of separate reasoning tools communicating and enhancing a proof development environment>
Evidential tool bus~\cite{DBLP:conf/icfem/Rushby05,fk:etb}.
Omega.
MathServe?
<This is a natural extension of the integration of automatic tools into interactive systems.>

>>>>

The idea of separate reasoning tools communicating to enhance a proof development environment is also being pursued in the Evidential Tool Bus~\cite{DBLP:conf/icfem/Rushby05,fk:etb} and the MathServe System~\cite{DBLP:conf/cade/ZimmerA06}.
This idea is a natural extension of the integration of automatic tools with interactive theorem provers.
